Molecular Gas Dynamics of the lensed wet-merger RXSJ1131-1123 at $z$=0.654

### 2016-06-19 WRITEUP/ms.tex
update code and paper after fixing the typo in z in model script

We then attempt to characterize the molecular gas kinematics using an
empirically-motivated disk model \citep[\eg][]{Courteau97a,Puech08a,Miller11a}:
\begin{equation}
V = V_0 + \frac{2}{\pi} V_{a} \arctan(\frac{R}{R_{t}}),
\end{equation}
where $V$ is the observed velocity, $V_0$ is the velocity at dynamical center,
$V_{a}$ is the asymptotic velocity, and $R_{t}$ is the ``turnover''
radius at which the rotation curve becomes flat.
We perform non-linear least square fitting using an orthogonal distance
regression to find the best-fit parameters,
taking into account the uncertainties in both velocity (channel width) and
distance offset. We also place an upper limit on $R_{t}$\,$<$15 kpc
to keep this parameter physical \citep[\eg][]{Puech08a,Miller11a}.
The parameter uncertainties are inferred based on Monte Carlo simulation
of 500 iterations, where the input parameters are perturbed
according to random Gaussian distributions of sigmas
corresponding to their uncertainties.
Using this model, we find $V_{a}$\,=\,975\,$\pm$\,387 \kms,
$R_{t}$\,=\,10.6\,$\pm$\,5.7\,kpc, and $V_0$\,=\,28\,$\pm$\,40 \kms.
However, since emission is not resolved along the flat regime
of the rotation curve, the asymptotic velocity is poorly constrained and
the ``turnover'' radius is at most a lower limit.
In particular, $V_{a}$ and $R_{t}$ are highly correlated with a
Pearson coefficient $R$\,=\,0.998, and 0.027 between $V_{a}$ and $V_0$.

@@

The asymptotic velocity ($V_{a}$) -- an extrapolation of the model
out to radius beyond the disk scale-length and half-light radius --
is not equivalent to maximum observed velocity ($V_{\rm max}$),
which is commonly used in literature to parameterize disc rotation.
The arctangent model is most commonly used in studies of the
Tully-Fisher relation, where an extrapolation to V$_{2.2}$ (velocity
at 2.2 disc scale-length or $\sim$1.375 half-light radius,
or $\sim$0.7$R_{\rm opt}$\footnote{Radius enclosing 83\% of the light
distribution.}) is typically adopted
as the rotation velocity ($V_{\rm max}$ in their
terminology) since this corresponds to the radius at which the velocity
of a pure exponential disc peaks.
We here adopt the maximum {\em observed} velocity
$V_{\rm rot}$\,=\,345\,$\pm$\,55\,\kms at 6\,$\pm$\,3\,kpc from the
dynamical center as a proxy to the rotation velocity.
This radius corresponds to $\sim$0.6$R_e$, where $R_e$ is the half-light
radius $\sim$10.3\,kpc inferred from the {\it HST} $I$-band
lens model (C06; converted to
our cosmology).
We note that the source plane half-light radius varies substantially with
wavelength. In particular, the half-light radius is found to be
$\sim$\,4kpc and $\sim$7\,kpc in $V$-band
\citep{Brewer08a} and $H$-band (C06), respectively.
This discrepancy arises owing to the exclusion of the more
diffused emission in $V$-band (rest-frame UV),
which traces young massive stars.
The $V$-band compactness may be explained in part
due to the fact that its emission is
more susceptible to dust extinction than other bands.
On the other hand, the molecular gas (fuel for \SF) is more compact
than the more evolved stellar population, as traced by $I$ and $H$-bands.
This is consistent with the picture that stars diffuse outward
after their formation \citep{Calzetti01a}.

>>>>

We then attempt to characterize the molecular gas kinematics using an
empirically-motivated disk model \citep[\eg][]{Courteau97a,Puech08a,Miller11a}:
\begin{equation}
V = V_0 + \frac{2}{\pi} V_{a} \arctan(\frac{R}{R_{t}}),
\end{equation}
where $V$ is the observed velocity, $V_0$ is the velocity at dynamical center,
$V_{a}$ is the asymptotic velocity, and $R_{t}$ is the ``turnover''
radius at which the rotation curve becomes flat.
We perform non-linear least square fitting using an orthogonal distance
regression to find the best-fit parameters,
taking into account the uncertainties in both velocity (channel width) and
distance offset. We also place an upper limit on $R_{t}$\,$<$15 kpc
to keep this parameter physical \citep[\eg][]{Puech08a,Miller11a}.
The parameter uncertainties are inferred based on Monte Carlo simulation
of 500 iterations, where the input parameters are perturbed
according to random Gaussian distributions of sigmas
corresponding to their uncertainties.
Using this model, we find $V_{a}$\,=\,975\,$\pm$\,387 \kms,
$R_{t}$\,=\,10.7\,$\pm$\,5.7\,kpc, and $V_0$\,=\,28\,$\pm$\,40 \kms.
However, since emission is not resolved along the flat regime
of the rotation curve, the asymptotic velocity is poorly constrained and
the ``turnover'' radius is at most a lower limit.
In particular, $V_{a}$ and $R_{t}$ are highly correlated with a
Pearson coefficient $R$\,=\,0.998, and 0.027 between $V_{a}$ and $V_0$.

@@

The asymptotic velocity ($V_{a}$) -- an extrapolation of the model
out to radius beyond the disk scale-length and half-light radius --
is not equivalent to maximum observed velocity ($V_{\rm max}$),
which is commonly used in literature to parameterize disc rotation.
The arctangent model is most commonly used in studies of the
Tully-Fisher relation, where an extrapolation to V$_{2.2}$ (velocity
at 2.2 disc scale-length or $\sim$1.375 half-light radius,
or $\sim$0.7$R_{\rm opt}$\footnote{Radius enclosing 83\% of the light
distribution.}) is typically adopted
as the rotation velocity ($V_{\rm max}$ in their
terminology) since this corresponds to the radius at which the velocity
of a pure exponential disc peaks.
We here adopt the maximum {\em observed} velocity
$V_{\rm rot}$\,=\,345\,$\pm$\,55\,\kms at 6\,$\pm$\,3\,kpc from the % line center velo of the reddest channel slice, unc = slice width
dynamical center as a proxy to the rotation velocity.
This radius corresponds to $\sim$0.6$R_e$, where $R_e$ is the half-light
radius $\sim$10.3\,kpc inferred from the {\it HST} $I$-band
lens model (C06; converted to
our cosmology).
We note that the source plane half-light radius varies substantially with
wavelength. In particular, the half-light radius is found to be
$\sim$\,4kpc and $\sim$7\,kpc in $V$-band
\citep{Brewer08a} and $H$-band (C06), respectively.
This discrepancy arises owing to the exclusion of the more
diffused emission in $V$-band (rest-frame UV),
which traces young massive stars.
The $V$-band compactness may be explained in part
due to the fact that its emission is
more susceptible to dust extinction than other bands.
On the other hand, the molecular gas (fuel for \SF) is more compact
than the more evolved stellar population, as traced by $I$ and $H$-bands.
This is consistent with the picture that stars diffuse outward
after their formation \citep{Calzetti01a}.
